Enforced Invariant Confluence

### 2017-01-27 doc/paper/alternativesproofs.tex
Showed 1-iconvergence does not imply 0-isafety.
This is a great result!

>>>>

\begin{claim}\label{clm:1-iconvergence-not-implies-0-isafety}
  1-\iconvergence{} $\centernot\implies$ 0-\isafety{}.
\end{claim}
\begin{proof}
  Let
    $I \defeq x = -42 \lor x \geq 0$ and
    $c \defeq \impif{read(x)\geq0}{add(x,1)}{}$.
  First, we show that $\set{c}$ is 1-\iconvergent{} with respec to $I$.
  Consider an arbitrary $D$,
    $D'$, $D''$, such that
    $I(D)$,
    $I(D')$,
    $I(D'')$,
    $I(D \circ \denote{c}(D'))$, and
    $I(D \circ \denote{c}(D''))$.
  We perform a case analysis on $D$.
  \begin{itemize}
    \item \textbf{Case 1: $D = -42$.}
      $D'$ and $D''$ must equal both equal $-42$. If either did not, say $D'$,
      then $D \circ \denote{c}(D')$ would be $-41$ which violates our
      assumption that $I(D \circ \denote{c}(D'))$. If both $D'$ and $D''$ equal
      $-42$, then $D \circ \denote{c}(D') \circ \denote{c}(D'') = -42$ which
      satisfies $I$.
    \item \textbf{Case 2: $D \geq 0$.}
      Depending on the value of $D'$ and $D''$, $D \circ \denote{c}(D') \circ
      \denote{c}(D'')$ could equal $D$, $D + 1$, or $D + 2$. All three of these
      datbases satisfy the invariant.
  \end{itemize}

  Next, we show that $\set{t_1}$ is not 0-\isafe{} with respect to $I$. Let $D
  = -42$ and $D = 0$. $I(D)$ and $I(D')$ but $D \circ \denote{c}(D') = -41$
  which does not satisfy the invariant.
\end{proof}
